Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
changes of table and companionship on memorability

% TODO explain tables
\begin{table*}[t]
	\centering
	\caption{Participant responses about the memorability, believability, and desirability of Rewinds and photos. The aggregate responses for the two mediums are compared.}
	\small
	\label{within-subject-table}
	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
		\cline{2-9}
		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Believability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
		& \begin{tabular}[c]{@{}c@{}}Rewinds\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}Photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}Rewinds\\ trip\end{tabular} & Photo & Rewinds & Photo & Rewinds \\ \hline
		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
		\multicolumn{1}{|c|}{\%} & 97 & \multicolumn{2}{c|}{0.50} & 54 & 78 & 80 & 11 & 15 \\ \hline
		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
	\end{tabular}
\end{table*}

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.58} & 0.51 & 0.47 & 1.00 & 1.00 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 1.00} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 10} & \cellcolor[HTML]{ACDDAA}72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 36} \\ \cline{3-17} 

@@

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compared to 55\% reported by participants who believed that they traveled in groups, with $\chi^2(1, N=94) = 31.812$, $p <.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and I walked a certain way -- don't usually take this route". Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1, N=133) = 9.016$, $p <.01)$.

>>>>

% TODO explain tables
\begin{table*}[t]
	\centering
	\caption{Participant responses about the memorability, believability, and desirability of Rewinds and photos. The aggregate responses for the two mediums are compared.}
	\small
	\label{within-subject-table}
	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
		\cline{2-9}
		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Believability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
		& \begin{tabular}[c]{@{}c@{}}Rewinds\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}Photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}Rewinds\\ trip\end{tabular} & Photo & Rewinds & Photo & Rewinds \\ \hline
		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
		\multicolumn{1}{|c|}{\%} & 97 & \multicolumn{2}{c|}{50} & 54 & 78 & 80 & 11 & 15 \\ \hline
		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
	\end{tabular}
\end{table*}

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 58} & 51 & 47 & 100 & 100 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 100} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 10} & \cellcolor[HTML]{ACDDAA}72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 36} \\ \cline{3-17} 

@@

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 100%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that trip remembrance is influenced by the presence of travel companions. Trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and I walked a certain way -- don't usually take this route". Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1, N=133) = 9.016$, $p <.01)$. For location rememberance, participants who believed that they traveled alone and those who believed that they traveled with companions all had a 100\% successful recalling rate. Note that this is because those who reported on their companionship were the ones that recognized the places from the images.
